---
title: "IterationCh21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(stringr)
```
#Ch 21 Iteration
## 21.2.1
1. 
```{r}
output <- vector("double", ncol(mtcars))
names(output) <- names(mtcars)
for (i in names(mtcars)) {
  output[i] <- mean(mtcars[[i]])
}
output
```
```{r}
output <- vector("list", ncol(nycflights13::flights))
names(output) <- names(nycflights13::flights)
for (i in names(nycflights13::flights)) {
  output[i] <- class(nycflights13::flights[[i]])
}
output
```
```{r}
data("iris")
iris_uniq <- vector("double", ncol(iris))
names(iris_uniq)<- names(iris)
for (i in names(iris)){
  iris_uniq[1] <- length(unique(iris[[i]]))
}
iris_uniq
```
```{r}
n <- 10
mu <- c(-10, 0, 10, 100)
normals <- vector("list", length(mu))
for (i in seq_along(normals)) {
  normals[[i]] <- rnorm(n, mean = mu[i])
}
normals
```
3.
```{r}
humps <- c("five", "four", "three", "two", "one", "no")
for (i in humps) {
  cat(str_c("Alice the camel has ", rep(i,3), " humps.", collapse = "\n"), "\n")
  if (i == "no") { cat("Now Alice is a horse.\n")} else{
    cat("So go, Alice, go.\n")
  }
  cat("\n")
}
```
```{r}
bottles<- function(n) {
  if (n>1) {
    str_c(n, "bottles")
  } else if (n == 1) {
    "1 bottle"
  } else {
    "no more bottles"
  }
}
beer_bottles <- function(total_bottles) {
  for (current_bottles in seq(total_bottles, 0)) {
    if (current_bottles > 0) {
      cat(str_c( "Take one down and pass it around, ", bottles(current_bottles - 1), " of beer on the wall.\n"))
    } else {cat(str_c("Go to the store and buy some more, ", bottles(total_bottles), " of cat(\n"))}
  }
}
beer_bottles(3)
```
##21.3.1
2. if there is no name for the vector, the it cannot run the loop. If there are duplicate names, then it will use the first
4. this code multiplies disp by 0.0163871 and replaces am with a factor variable
##21.4.1
1. returns a vector or array or list of values obtained by applying a function to margins of an array or matrix.
2. 
```{r}
col_summary2 <- function(df, fun) {
  numeric_cols <- vector("logical", length(df))
  for (i in seq_along(df)) {
    numeric_cols[[i]] <- is.numeric(df[[i]])
  }
  idxs <- which(numeric_cols)
  n <- sum(numeric_cols)
  out <- vector("double", n)
  for (i in seq_along(idxs)){
    out[[i]] <- fun(df[[idxs[[i]]]]) 
  }
  names(out) <- names(df)[idxs]
  out
}
```
##21.5.1
2. map function
3.map will work on any function. it runs through all the numbers 1 through 5 and the runif makes it use that number as the first argument

